---
title: "Weekly Statistics"
author: 'Siaya County - Household Sample'
date: ''
output:
  html_document:
    theme: paper
    toc: FALSE
    includes:
      before_body: header.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(haven)
library(tidyverse)
library(dygraphs)
library(xts)
library(ggplot2)
library(rjson) #reading shapefiles for heatmaps
library(plotly) #interactive visualization

end_week = "20"
end_survey = "August 22"
loans_weekly <- read_dta("../../GE_Endline2/covid19/data/temp_loans_weekly.dta") # name changed, dropped the "All"

loans <- c("week", "loantype_1", "loantype_2" , "loantype_3", "loantype_4", "loantype_5" , "loantype_6")
loans <- loans_weekly[loans]

loans1 <- c("week", "loantype_1" , "loantype_3" , "loantype_6")
loans1 <- loans_weekly[loans1]
loans2 <- c("week", "loantype_2", "loantype_4", "loantype_5")
loans2 <- loans_weekly[loans2]

tookloan <- c("week", "tookloan_0", "tookloan_1")
tookloan <- loans_weekly[tookloan]

presAnnotation <- function(dygraph, x, text) {
  dygraph %>%
    dyAnnotation(x, text, attachAtBottom = TRUE, width = 70, height = 25)
}

```

<font size="5">**Took a loan**</font>   
We ask "In the past 14 days, did anyone in this household take out a new loan for use on household consumption?"
```{r tookloan}
it_g  <- dygraph(tookloan, main = "") %>%
  dySeries("tookloan_0", strokeWidth = 4, label = "No") %>%
  dySeries("tookloan_1", strokeWidth = 4, label = "Yes") %>%  
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE , label = "Percentage of sample", valueRange = c(0, 110)) %>% 
  dyOptions(stackedGraph =TRUE , axisLineWidth = 4, includeZero = TRUE,drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(6, "Set2"), connectSeparatedPoints = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation(end_week, text = end_survey) %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyEvent(-1 , "February", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
  dyEvent(0 , "Lockdown begins March 15", labelLoc = "top") %>%
    dyEvent(11 , "Round 2 of Survey", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
  dyLegend(width = 100, labelsSeparateLines = FALSE) 
it_g
```

<font size="5">**Type of loan taken**</font>  
"If yes, what kind of loan?"
```{r loans1}
it_g  <- dygraph(loans1, main = "") %>%
  dySeries("loantype_1", strokeWidth = 4, label = "Loan from a friend / relative") %>%
  dySeries("loantype_3", strokeWidth = 4, label = "Mobile lending") %>%
  dySeries("loantype_6", strokeWidth = 4, label = "Merry-go-round / ROSCA") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE , label = "Percentage of loans taken") %>% 
  dyOptions(axisLineWidth = 4, includeZero = TRUE,drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(6, "Set1"), connectSeparatedPoints = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation(end_week, text = end_survey) %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyEvent(-1 , "February", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
  dyEvent(0 , "Lockdown begins March 15", labelLoc = "top") %>%
    dyEvent(11 , "Round 2 of Survey", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
  dyLegend(width = 600, labelsSeparateLines = FALSE) 
it_g
```

```{r loans2}
it_g  <- dygraph(loans2, main = "") %>%
  dySeries("loantype_2", strokeWidth = 4, label = "Commercial bank / commercial lender") %>%
  dySeries("loantype_4", strokeWidth = 4, label = "Money lender / shylock") %>%  
  dySeries("loantype_5", strokeWidth = 4, label = "SACCO") %>% 
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE , label = "Percentage of loans taken") %>% 
  dyOptions(axisLineWidth = 4, includeZero = TRUE,drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(6, "Set2"), connectSeparatedPoints = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation(end_week, text = end_survey) %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyEvent(-1 , "February", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
  dyEvent(0 , "Lockdown begins March 15", labelLoc = "top") %>%
    dyEvent(11 , "Round 2 of Survey", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
  dyLegend(width = 650, labelsSeparateLines = FALSE) 
it_g
```



These data comes from phone survey interviews conducted by [REMIT Kenya](http://remitkenya.co.ke/) in Siaya County, Kenya. We are collecting data for a sample of ~11,000 households in the county, which is representative of the whole population. At the same time, our weekly sampling method assures weekly representativeness of the overall sample.

So far we have conducted 15,832 household surveys, with the following distribution per week:

| Week	| Dates	| Number of surveys | Survey round |
|------|:-----:|:---------:|:-------:|
| Week 1 |	05 April 2020 - 11 April 2020	| 745 | 1 |
| Week 2 |	12 April 2020 - 18 April 2020	| 744 | 1|
| Week 3 |	19 April 2020 - 25 April 2020	| 1,478 |1|
| Week 4 |	26 April 2020 - 02 May 2020	| 1,146 |1|
| Week 5 |	03 May 2020 - 09 May 2020	| 1,499 |1|
| Week 6 |	10 May 2020 - 16 May 2020	| 986 |1|
| Week 7 |	17 May 2020 - 23 May 2020	| 1,217 |1|
| Week 8 |	24 May 2020 - 30 May 2020	| 771 |1|
| Week 12 |	21 June 2020 - 27 June 2020	| 1747 |2|
| Week 14 |	5 July 2020 - 11 July 2020	| 1087 |2|
| Week 15 |	12 July 2020 - 18 July 2020	| 611 |2|
| Week 16 |	19 July 2020 - 25 July 2020	| 889 |2|
| Week 17 |	26 July 2020 - 1 August 2020	| 820 |2|
| Week 18 |	2 August 2020 - 9 August 2020	| 870 |2|
| Week 19 |	10 August 2020 - 17 August 2020	| 836 |2|
| Week 20 |	18 August 2020 - 25 August 20200	| 384 |2|


