---
title: "Weekly Statistics"
author: 'Siaya County - Enterprise Sample'
date: ''
output:
  html_document:
    theme: paper
    toc: FALSE
    includes: 
      before_body: header.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(haven)
library(tidyverse)
library(dygraphs)
library(xts)
ent_weekly <- read_dta("~/Dropbox (Princeton)/GE_Endline2/covid19/data/COVID_AllENTs_outcomes_weekly.dta")


#Grouping vars for graphs
rev <- c("week", "rev_wins")
rev <- ent_weekly[rev]

profits <- c("week", "profits_wins")
profits <- ent_weekly[profits]

op <- c("week", "op", "temp_closed", "perm_closed")
op <- ent_weekly[op]

inv <- c("week", "investment_wins")
inv <- ent_weekly[inv]

wages <- c("week", "wages_wins")
wages <- ent_weekly[wages]

cov <- c("week", "ecov_1", "ecov_2", "ecov_3")
cov <- ent_weekly[cov]

presAnnotation <- function(dygraph, x, text) {
  dygraph %>%
    dyAnnotation(x, text, attachAtBottom = TRUE, width = 60, height = 25)
}

```

  
##  {.tabset}

### Operations  
<font size="5">**Enterprise status**</font>
``` {r op}
  op_g <- dygraph(op, main = "") %>%
  dySeries("perm_closed", strokeWidth = 4, label = "Permanently closed") %>%
  dySeries("temp_closed", strokeWidth = 4, label = "Temporarily closed") %>%
  dySeries("op", strokeWidth = 4, label = "Operational") %>%
  dyAxis("x", pixelsPerLabel = 90 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Percentage of sample", drawGrid = FALSE, valueRange = c(0, 110)) %>% 
  dyLegend(width = 500, labelsSeparateLines = FALSE) %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set1")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "May 10") %>%
  presAnnotation("4", text = "June 02") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
op_g
```
  
  

*** 
### Revenue and profit  
<font size="5">**Revenue (USD, PPP) - past 14 days**</font>
``` {r revenue}
  rev_g <- dygraph(rev, main = "") %>%
  dySeries("rev_wins", strokeWidth = 4, label = "Revenue") %>%
  dyAxis("x", pixelsPerLabel = 90 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "USD, PPP", drawGrid = FALSE) %>% 
  dyLegend(width = 250, labelsSeparateLines = FALSE) %>%
  dyOptions(stackedGraph = FALSE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set1")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "May 10") %>%
  presAnnotation("4", text = "June 02") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
rev_g
```
  
  

***  

<font size="5">**Profits (USD, PPP) - past 14 days**</font>
``` {r profits}
  profits_g <- dygraph(profits, main = "") %>%
  dySeries("profits_wins", strokeWidth = 4, label = "Profits") %>%
  dyAxis("x", pixelsPerLabel = 90 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "USD, PPP", drawGrid = FALSE) %>% 
  dyLegend(width = 250, labelsSeparateLines = FALSE) %>%
  dyOptions(stackedGraph = FALSE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set2")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "May 10") %>%
  presAnnotation("4", text = "June 02") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
profits_g
```
  
  

*** 

### Investment and wages

<font size="5">**Investment (USD, PPP) - past 14 days**</font>
``` {r invest}
  inv_g <- dygraph(inv, main = "") %>%
  dySeries("investment_wins", strokeWidth = 4, label = "Investment") %>%
  dyAxis("x", pixelsPerLabel = 90 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "USD, PPP", drawGrid = FALSE) %>% 
  dyLegend(width = 250, labelsSeparateLines = FALSE) %>%
  dyOptions(stackedGraph = FALSE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set1")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "May 10") %>%
  presAnnotation("4", text = "June 02") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
inv_g
```
  
  ***  
  
  
<font size="5">**Wages (USD, PPP) - past 14 days**</font>
``` {r wages}
  wages_g <- dygraph(wages, main = "") %>%
  dySeries("wages_wins", strokeWidth = 4, label = "Wages") %>%
  dyAxis("x", pixelsPerLabel = 90 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "USD, PPP", drawGrid = FALSE) %>% 
  dyLegend(width = 250, labelsSeparateLines = FALSE) %>%
  dyOptions(stackedGraph = FALSE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set2")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "May 10") %>%
  presAnnotation("4", text = "June 02") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
wages_g
```

  
***     


### COVID-19  
<font size="5">**COVID-19 Impact**</font>

How has COVID-19 affected this business?*  

``` {r ecov}
  ecov_g <- dygraph(cov, main = "") %>%
  dySeries("ecov_1", strokeWidth = 4, label = "Reduction in demand/customers") %>%
  dySeries("ecov_2", strokeWidth = 4, label = "Has not affected") %>%
  dySeries("ecov_3", strokeWidth = 4, label = "Other") %>%
  dyAxis("x", pixelsPerLabel = 90 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "USD, PPP", drawGrid = FALSE) %>% 
  dyLegend(width = 500, labelsSeparateLines = FALSE) %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set1")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("0.5", text = "May 10") %>%
  presAnnotation("4.5", text = "June 02") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
ecov_g
```
    
*This is for the proportion of enterprises currently operating.  

  ***  
  
## {}
      
These data comes from phone survey interviews conducted by [REMIT Kenya](http://remitkenya.co.ke/) in Siaya County, Kenya. We are collecting data for a sample of ~5,000 enterprises in the county, which is representative of the whole population of enterprises. At the same time, our weekly sampling method assures weekly representativeness of the overall sample.

So far we have interviewed 1,770 enterprises, with the following distribution per week:

| Week	| Dates	| Number of surveys |
|------|:-----:|:---------:|
| Week 1 |	10 May 2020 - 16 May 2020	| 542 |
| Week 2 |	17 May 2020 - 23 May 2020	| 495 |
| Week 3 |	24 May 2020 - 30 May 2020	| 464 |
| Week 4 |	31 May 2020 - 02 Jun 2020	| 269 |



