---
title: "Weekly Statistics"
author: 'Siaya County - Household Sample'
date: ''
output:
  html_document:
    theme: paper
    toc: FALSE
    includes: 
      before_body: header.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(haven)
library(tidyverse)
library(dygraphs)
library(xts)
library(ggplot2)
library(rjson) #reading shapefiles for heatmaps
library(plotly) #interactive visualization


## Importing Data ##
#covid_weekly <- read_dta("~/Dropbox (Princeton)/GE_Endline2/covid19/data/COVID_AllHHs_outcomes_weekly.dta")
covid_weekly <- read_dta("../../GE_Endline2/covid19/data/COVID_AllHHs_outcomes_weekly.dta")

covid_price_index <- read.csv("../../GE_Endline2/covid19/data/COVID_PriceIndex_Heatmap.csv", header = T)
covid_price_index["Price Index"] <- covid_price_index$price_index_median
covid_price_index$subloc_name <- as.character(covid_price_index$subloc_name)

covid_subloc <- read_csv("../../GE_Endline2/covid19/data/COVID_AllHHs_outcomes_heatmap.csv")
covid_subloc$subloc_name <- as.character(covid_subloc$subloc_name)
covid_subloc <- covid_subloc[complete.cases(covid_subloc[ , 2]),] #drops observations with missing week values
covid_subloc$`Total Consumption` <- covid_subloc$c4_wins
covid_subloc$`Total Income` <- covid_subloc$i4_wins
covid_subloc$`Face mask usage` <- covid_subloc$ckn6_mask_wins

json_file <- rjson::fromJSON(file="../../GE_Endline2/covid19/covid_map/SampleAreaSublocations_clean.geojson")

#Grouping vars for graphs
cov <- c("week", "cov1_wins", "cov3_wins", "cov4_wins")
cov <- covid_weekly[cov]

cov1 <- c("week", "cov1_cough_wins", "cov1_fever_wins", "cov1_tired_wins", "cov1_fever_cough_wins")
cov1 <- covid_weekly[cov1]

ckn <- c("week", "ckn2_wins", "ckn3_wins", "ckn4_wins", "ckn5_wins", "ckn6_wins")
ckn <- covid_weekly[ckn]

ckn2 <- c("week", "ckn2_cough_wins", "ckn2_fever_wins", "ckn2_tired_wins", "ckn2_dbreath_wins")
ckn2 <- covid_weekly[ckn2]

ckn6 <- c("week", "ckn6_washhands_wins", "ckn6_sanitizer_wins", "ckn6_stayhome_wins", "ckn6_mask_wins")
ckn6 <- covid_weekly[ckn6]

c <- c("week", "c1a_wins", "c1b_wins", "c3_wins") #, "c3_wins", "c4_wins"
c <- covid_weekly[c]

i <- c("week", "i1_wins", "i2_wins" , "i3_wins") #, "i4_wins", "i5_wins", "i6_wins"  , "i7_wins"
i <- covid_weekly[i]
d <- c("week", "i7_wins") 
d <- covid_weekly[d]

it <- c("week", "i5a_wins", "i5b_wins" , "i5c_wins")
it <- covid_weekly[it]

f1 <- c("week", "f1_h_shortages_wins", "f1_h_price_wins", "f1_h_income_wins")
f1 <- covid_weekly[f1]


f1a <- c("week", "f1_h_going_wins", "f1_h_reduce_wins", "f1_h_closed_wins")
f1a <- covid_weekly[f1a]

f1_d <- c("week", "f1_d_skippedadult_wins", "f1_d_skippedchild_wins")
f1_d <- covid_weekly[f1_d]

f1_meals <- c("week", "f1_meat_wins", "f1_eggs_wins")
f1_meals <- covid_weekly[f1_meals]

net5 <- c("week", "net5_today_wins", "net5_last7_wins", "net5_last14_wins")
net5 <- covid_weekly[net5]

ch <- c("week", "ch1_wins", "ch2_wins", "ch3_wins")
ch <- covid_weekly[ch]

l <- c("week", "l1_wins", "l2_wins", "l3_wins")
l <- covid_weekly[l]

e <- c("week", "e3_wins", "e4_wins")
e <- covid_weekly[e]

tg <- c("week", "tg1", "tg2", "tg3", "tg4", "tg5")
tg <- covid_weekly[tg]

tp <- c("week", "tp1", "tp2", "tp3")
tp <- covid_weekly[tp]

gv <- c("week", "gv1", "gv2", "gv3")
gv <- covid_weekly[gv]

v <- c("week", "gv4", "gv5")
v <- covid_weekly[v]

#PRICES
#services
ps <- c("week", "mean_price_11", "mean_price_111", "mean_price_113") #"Adult head shaving (1)", "Fixing a small hole at a tailor (1)", "Grinding 1kg of maize"
ps <- covid_weekly[ps]

#livestock
pl <- c("week", "mean_price_18", "mean_price_16", "mean_price_112") #"Chicken hen (1)", "Calf - local (1)", "Goat (1)"
pl <- covid_weekly[pl]

#food1
pf1 <- c("week", "mean_price_12", "mean_price_14", "mean_price_15", "mean_price_119") #"Banana - sweet (bunch)", "Beans (2kg)", "Beef meat (1kg)", "Tilapia fish (whole)"
pf1 <- covid_weekly[pf1]

#food2
pf2 <- c("week", "mean_price_19", "mean_price_114", "mean_price_117", "mean_price_118") # "Cooking fat (500g)", "Maize (2kg)", "Rice (1kg)", "Sugar (1kg)"
pf2 <- covid_weekly[pf2]

#food3
pf3 <- c("week", "mean_price_110", "mean_price_115", "mean_price_120") # "Egg (one)", "Onions (4)", "Tomatoes (4)"
pf3 <- covid_weekly[pf3]

#non food
pnf <- c("week", "mean_price_13", "mean_price_17", "mean_price_116") #"Bar soap (1)", "Charcoal (2kg)", "Panadol (pair)"
pnf <- covid_weekly[pnf]

#MENTAL HEALTH
#cesd_10
cesd_10<- c("week", "cesd")
cesd_10 <- covid_weekly[cesd_10]
#nervious, anxious or on edge
mh1 <- c("week", "s6_q1_1", "s6_q1_2", "s6_q1_3", "s6_q1_4")
mh1 <- covid_weekly[mh1]
#depressed
mh2 <- c("week", "s6_q2_1", "s6_q2_2", "s6_q2_3", "s6_q2_4")
mh2 <- covid_weekly[mh2]
#lonely
mh3 <- c("week", "s6_q3_1", "s6_q3_2", "s6_q3_3", "s6_q3_4")
mh3 <- covid_weekly[mh3]
#hopeful about the future
mh4 <- c("week", "s6_q4_1", "s6_q4_2", "s6_q4_3", "s6_q4_4")
mh4 <- covid_weekly[mh4]
#physical reactions due to COVID-19
mh5 <- c("week", "s6_q5_1", "s6_q5_2", "s6_q5_3", "s6_q5_4")
mh5 <- covid_weekly[mh5]

presAnnotation <- function(dygraph, x, text) {
  dygraph %>%
    dyAnnotation(x, text, attachAtBottom = TRUE, width = 60, height = 25)
}

```

  
##  {.tabset}

### Income  
<font size="5">**Earnings per capita (USD, PPP) - past 14 days**</font>
``` {r income}
  i_g <- dygraph(i, main = "") %>%
  dySeries("i3_wins", strokeWidth = 4, label = "Wage earnings") %>%
  dySeries("i2_wins", strokeWidth = 4, label = "Self-employment earnings") %>%
  dySeries("i1_wins", strokeWidth = 4, label = "Agricultural earnings") %>%
  #  dySeries("i7_wins", strokeWidth = 4, label = "Dissaving") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "USD, PPP", drawGrid = FALSE) %>% 
  dyLegend(width = 250, labelsSeparateLines = TRUE) %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set2")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
i_g
```
  

  This plot aggregates income from each of the three earning sources, across all working-age household members, stacking them to add to the average earning per capita, including children, in the past 14 days. If the household does not perceive income from one or more of the sources, those data points are assigned zeros to assure representativeness for the whole population.  
   
***  
  
<font size="5">**Dissaving per capita (USD, PPP) - past 14 days**</font>  
 The dissaving variable is constructed by adding the value of assets sold and loans taken, and substracting the value of any assets or durables bought.  

```{r dissaving}
d_g  <- dygraph(d, main = "") %>%
  dySeries("i7_wins", strokeWidth = 4, label = "Dissaving") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE , label = "USD, PPP") %>% 
  dyOptions(axisLineWidth = 4, includeZero = TRUE,drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set1")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyLegend(width = 210, show="always") 
d_g
```

   
***  
   
  <font size="5">**Transfers per capita (USD, PPP) - past 14 days**</font>  
    We ask whether in the past 14 days anyone in the household received a gift/assistance of money or goods, and its value, from (i) the government, (ii) from a non-governmental organization or community group, or (iii) from an individual politican or government official.  

```{r transfers}
it_g  <- dygraph(it, main = "") %>%
  dySeries("i5a_wins", strokeWidth = 4, label = "Government") %>%
  dySeries("i5b_wins", strokeWidth = 4, label = "NGO or community group") %>%
  dySeries("i5c_wins", strokeWidth = 4, label = "Politicians") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE , label = "USD, PPP") %>% 
  dyOptions(axisLineWidth = 4, includeZero = TRUE,drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set1")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyLegend(width = 500, labelsSeparateLines = FALSE) 
it_g
```
  

  
*** 

### Consumption

<font size="5">**Weekly consumption per capita (USD, PPP)**</font>
``` {r consumption}
c_g <- dygraph(c, main = "", group = "Siaya County Sample") %>%
  #dySeries("c4_wins", strokeWidth = 6, label = "Total consumption") %>%
  dySeries("c3_wins", strokeWidth = 4, label = "Non-food expenditure") %>%
  dySeries("c1a_wins", strokeWidth = 4, label = "Food expenditure") %>%
  dySeries("c1b_wins", strokeWidth = 4, label = "Own-food consumption") %>%
  #dySeries("c1_wins", strokeWidth = 4, label = "Food expenditure") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "USD, PPP", drawGrid = FALSE) %>% 
  dyLegend(width = 250 , labelsSeparateLines = TRUE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set2")) %>%
      dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  c_g

```
Own-food consumption accounts for own agricultural and pastoral production at market value.  

*** 

### Food Security  
<font size="5">**Number of days skipping meals in the past 7 days**</font>  

```{r struggles}
f1_d_g  <- dygraph(f1_d, main = "") %>%
  dySeries("f1_d_skippedadult_wins", strokeWidth = 4, label = "Adults skipped meals") %>%
  dySeries("f1_d_skippedchild_wins", strokeWidth = 4, label = "Children skipped meals") %>%
 # dySeries("f1_d_hungryadult", strokeWidth = 4, label = "Adults gone to bed hungry") %>%
#  dySeries("f1_d_hungrychild", strokeWidth = 4, label = "Children gone to bed hungry") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE , label = "Number of days") %>% 
  dyOptions(axisLineWidth = 4, includeZero = TRUE,drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set1")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyLegend(width = 210, labelsSeparateLines = TRUE) 
f1_d_g
```
     
***  
  
<font size="5">**Percentage of sample unable to buy usual amount of food due to:**</font>  
 We ask whether in the past 7 days, any household member was unable to buy the amount of food they usually buy because of: (i) price of food being too high, (ii) household income having dropped, and (iii) shortages in markets.  
   
 
   
```{r struggles2}
f1_g  <- dygraph(f1, main = "") %>%
  dySeries("f1_h_price_wins", strokeWidth = 4, label = "High food prices") %>%
  dySeries("f1_h_income_wins", strokeWidth = 4, label = "Income drop") %>%
  dySeries("f1_h_shortages_wins", strokeWidth = 4, label = "Shortages in markets") %>%
  dyAxis("x", pixelsPerLabel = 75 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE , label = "Percentage of sample") %>% 
  dyOptions(axisLineWidth = 4, includeZero = TRUE,drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set1")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("3", text = "April 25") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyLegend(width = 450, labelsSeparateLines = FALSE) %>% 
  dyRangeSelector(dateWindow = c("2", "9"))
f1_g
```   
 
     
***  
   
   <font size="5">**Other food hardship experiences, percentage of sample**</font>  
    We ask whether in the past 7 days, any household member experienced: (i) having to reduce the number of meals and/or the portion of each meal they would usually eat, (ii) difficulties in going to food markets due to mobility restrictions imposed by government, and (iii) difficulties in buying food due to most food markets being closed.  
    
  
```{r struggles3}
f1a_g  <- dygraph(f1a, main = "") %>%
  dySeries("f1_h_reduce_wins", strokeWidth = 4, label = "Had to reduce meals") %>%
  dySeries("f1_h_going_wins", strokeWidth = 4, label = "Mobility restrictions impede going to market") %>%
  dySeries("f1_h_closed_wins", strokeWidth = 4, label = "Closed food markets") %>%
  dyAxis("x", pixelsPerLabel = 75 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE , label = "Percentage of sample") %>% 
  dyOptions(axisLineWidth = 4, includeZero = TRUE,drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set2")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("3", text = "April 25") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyLegend(width = 475, labelsSeparateLines = FALSE) %>% 
  dyRangeSelector(dateWindow = c("2", "9"))
f1a_g
``` 
 
   
***  
### Household enterprises  
<font size="5">**Enterprises revenue and profits in the past 14 days**</font>
```{r enterprises}
e_g  <- dygraph(e, main = "") %>%
  dySeries("e3_wins", strokeWidth = 4, label = "Total enterprise revenue") %>%
  dySeries("e4_wins", strokeWidth = 4, label = "Total enterprise profits") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE , label = "USD, PPP") %>% 
  dyOptions(axisLineWidth = 4, includeZero = TRUE,drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set1")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyLegend(width = 200, labelsSeparateLines = TRUE) 
e_g
``` 
  
  ***  

### COVID-19  

<font size="5">**Reported COVID-19 Behavior Adoption**</font>    
We ask respondents whether they have changed their behavior in any way since learning about COVID-19, and if so, how  it has changed.

```{r behavior_changes}
  ckn6_g <- dygraph(ckn6, main = "") %>%
    dySeries("ckn6_washhands_wins", strokeWidth = 4, label = "Hand Washing") %>%
    dySeries("ckn6_mask_wins", strokeWidth = 4, label = "Face Mask") %>%    
    dySeries("ckn6_stayhome_wins", strokeWidth = 4, label = "Stay Home") %>%
    dySeries("ckn6_sanitizer_wins", strokeWidth = 4, label = "Hand Sanitizer") %>%
    dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
    dyAxis("y", drawGrid = FALSE, label = "Percentage of sample") %>% #grid
    dyLegend(width = 580) %>%
    dyOptions(axisLineWidth = 4, includeZero = TRUE, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set2")) %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
    dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
    dyEvent(1.7 , "Face masks mandatory", labelLoc = "bottom") %>%
  dyCrosshair(direction = "vertical")
  ckn6_g
```
   
    
***  

<font size="5">**Reported COVID-19 Symptoms, past 14 days**</font>  
We ask respondents whether they have experienced any illnesses or symptoms of a given list in the past 14 days.  
  

``` {r symptoms}
  cov1_g <- dygraph(cov1, main = "") %>% 
  dySeries("cov1_fever_wins", strokeWidth = 4, label = "Fever") %>%
  dySeries("cov1_tired_wins", strokeWidth = 4, label = "Tired") %>%
  dySeries("cov1_cough_wins", strokeWidth = 4, label = "Cough") %>%
  dySeries("cov1_fever_cough_wins", strokeWidth = 4, label = "Fever+Cough") %>%
    dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
    dyAxis("y", drawGrid = FALSE, label = "Percentage of sample") %>% #grid
  dyLegend(width = 500) %>%
  dyOptions(axisLineWidth = 4, includeZero = TRUE, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set2")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
  cov1_g
```
  
  

*** 

<font size="5">**Number of in-person interactions (other than HH members)**</font>  
  We ask: "Taken together, how many people outside this household have you interacted with in-person?"   

```{r interactions}
net5_g  <- dygraph(net5, main = "") %>%
  dySeries("net5_last14_wins", strokeWidth = 4, label = "In the past 14 days") %>%
  dySeries("net5_last7_wins", strokeWidth = 4, label = "In the past 7 days") %>%
  dySeries("net5_today_wins", strokeWidth = 4, label = "Today") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE, label = "Number of people") %>% 
  dyLegend(width = 500) %>%
     dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
 dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyOptions(axisLineWidth = 4, includeZero = TRUE, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set1"))
net5_g
```
  

*** 
  
### Labor Supply

<font size="5">**Weekly labor supply (hours per household adult)**</font>
``` {r labor}
l_g <- dygraph(l, main = "", group = "Siaya County Sample") %>%
  dySeries("l1_wins", strokeWidth = 4, label = "Agricultural labor supply") %>%
  dySeries("l3_wins", strokeWidth = 4, label = "Wage labor supply") %>%
  dySeries("l2_wins", strokeWidth = 4, label = "Own enterprise labor supply") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Hours per adult household member", drawGrid = FALSE) %>% 
  dyLegend(width = 550 , labelsSeparateLines = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set2")) %>%
      dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  l_g

```
  
  This plot aggregates hours worked on each of the three sources, across all working-age household members, stacking them to add to the average weekly labor supply per household adult. If the household does not work any hours on one or more of the labor categories, those data points are assigned zeros to assure representativeness of the whole population. 

***  
### Children Education  

<font size="5">**Children educational activities**</font>  
     We ask what has each child been doing over the last 15 minutes, whether the child has done any learning-related activities in the past 24 hours, and if so, what kind of activity. From this question we also learn whether the child attended school.
```{r children}
ch_g  <- dygraph(ch, main = "", group = "Siaya County Sample") %>%
  dySeries("ch3_wins", strokeWidth = 4, label = "Attended school in past 24hrs") %>%
  dySeries("ch2_wins", strokeWidth = 4, label = "Any learning in past 24hrs") %>%
  dySeries("ch1_wins", strokeWidth = 4, label = "Any learning in past 15mins") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE, label = "Percentage of sample") %>% 
     dyCrosshair(direction = "vertical") %>%
 dyLegend(width = 570) %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyOptions(axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set1"))
ch_g
```

   
   
***  
  
### Household Violence


<font size="5">**Gender violence**</font>

We ask married/cohabitant female respondents whether their husband/partner has (i) threaten to harm them or someone close to them, (ii) hit, slapped, kicked, or physically hurt them, and (iii) forced them to perform sexual acts.*  
```{r gender}
gv_g  <- dygraph(gv, main = "", group = "Siaya County Sample") %>%
  dySeries("gv1", strokeWidth = 4, label = "Threaten to harm them") %>%
  dySeries("gv2", strokeWidth = 4, label = "Physically hurt them") %>%
  dySeries("gv3", strokeWidth = 4, label = "Forced them to perform sexual acts") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE, label = "Percentage of married/cohabitant females") %>% 
     dyCrosshair(direction = "vertical") %>%
 dyLegend(width = 580) %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyOptions(axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set1"))
gv_g
```
  *This plot shows data only for the share of female respondents that were surveyed by a female field officer, and are currently married or living with a partner. This sub-sample accounts for ~55% of all married/cohabitant females in the study sample, and ~36% of all females.  
     
***  
  
<font size="5">**Violence in the household**</font>  
We ask: (i) Over the past 14 days, has there been a higher than usual amount of fights with members of your household?, and (ii) In the past 14 days, did you or your partner ever beat any of the children living in this household?  
```{r violence}
v_g  <- dygraph(v, main = "", group = "Siaya County Sample") %>%
  dySeries("gv4", strokeWidth = 4, label = "Children were beaten") %>%
  dySeries("gv5", strokeWidth = 4, label = "More fights than usual") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE, label = "Percentage of sample") %>% 
     dyCrosshair(direction = "vertical") %>%
 dyLegend(width = 350) %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyOptions(axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set1"))
v_g
```


***  

### Trust

<font size="5">**Trust in government**</font>  

How much do you trust your country’s government to take care of its citizens?  
``` {r trustgov}
tg_g <- dygraph(tg, main = "", group = "Siaya County Sample") %>%
  dySeries("tg1", strokeWidth = 4, label = "Strongly distrust") %>%
  dySeries("tg2", strokeWidth = 4, label = "Somewhat distrust") %>%
  dySeries("tg3", strokeWidth = 4, label = "Neither trust nor distrust") %>%
  dySeries("tg4", strokeWidth = 4, label = "Somewhat trust") %>%
  dySeries("tg5", strokeWidth = 4, label = "Strongly trust") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Percentage of sample", drawGrid = FALSE, valueRange = c(0, 110)) %>% 
  dyLegend(width = 450 , labelsSeparateLines = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set2")) %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
      dyCrosshair(direction = "vertical") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  tg_g

```
   
***   
  
  <font size="5">**Trust in other people**</font>  

Generally speaking, would you say that most people can be trusted or that you need to be very careful in dealing with people?  
``` {r trustpeople}

tp_g <- dygraph(tp, main = "", group = "Siaya County Sample") %>%
  dySeries("tp3", strokeWidth = 4, label = "Need to be careful") %>%
  dySeries("tp2", strokeWidth = 4, label = "Most people can be trusted") %>%
  dySeries("tp1", strokeWidth = 4, label = "Don't know") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Percentage of sample", drawGrid = FALSE, valueRange = c(0, 110)) %>% 
  dyLegend(width = 500 , labelsSeparateLines = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set1")) %>%
      dyCrosshair(direction = "vertical") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  tp_g

```


*** 

### Mental health


<font size="5">**Depression, CES-D-10**</font>  

**The Centre for Epidemiological Studies Depression Scale** (CES-D-10) is a 10-item Likert scale questionnaire assessing depressive symptoms in the past week. It includes three items on depressed affect, five items on somatic symptoms, and two on positive affect. Options for each item range from “rarely or none of the time” (score of 0) to “all of the time” (score of 3). Scoring is reversed for positive affect statements. Total scores can range from 0 to 30. **Higher scores suggest greater severity of symptoms.**  

``` {r cesd10}
cesd_g <- dygraph(cesd_10, main = "", group = "Siaya County Sample") %>%
  dySeries("cesd", strokeWidth = 4, label = "CES-D score") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Average score", drawGrid = FALSE) %>% 
  dyLegend(width = 450 , labelsSeparateLines = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(stackedGraph = FALSE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set2")) %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
      dyCrosshair(direction = "vertical") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  cesd_g

```
   
***  

We also ask questions 1-5 on core mental health from the John Hopkins Bloomberg School of Public Health (JHSPH) [resource](https://www.elizabethstuart.org/files/MH_survey-items-request_03_20.pdf).  

<font size="5">**Nervious, anxious or on edge**</font>  

In the past 7 days, how often have you felt nervous, anxious, or on edge?  
``` {r mh1}
mh1_g <- dygraph(mh1, main = "", group = "Siaya County Sample") %>%
  dySeries("s6_q1_4", strokeWidth = 4, label = "5-7 days") %>%
  dySeries("s6_q1_3", strokeWidth = 4, label = "3-4 days") %>%
  dySeries("s6_q1_2", strokeWidth = 4, label = "1-2 days") %>%
  dySeries("s6_q1_1", strokeWidth = 4, label = "Not at all or less than one day") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Percentage of sample", drawGrid = FALSE, valueRange = c(0, 110)) %>% 
  dyLegend(width = 450 , labelsSeparateLines = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set2")) %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
      dyCrosshair(direction = "vertical") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  mh1_g

```
   
*** 
<font size="5">**Depressed**</font>    

In the past 7 days, how often have you felt depressed?  

``` {r mh2}
mh2_g <- dygraph(mh2, main = "", group = "Siaya County Sample") %>%
  dySeries("s6_q2_4", strokeWidth = 4, label = "5-7 days") %>%
  dySeries("s6_q2_3", strokeWidth = 4, label = "3-4 days") %>%
  dySeries("s6_q2_2", strokeWidth = 4, label = "1-2 days") %>%
  dySeries("s6_q2_1", strokeWidth = 4, label = "Not at all or less than one day") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Percentage of sample", drawGrid = FALSE, valueRange = c(0, 110)) %>% 
  dyLegend(width = 450 , labelsSeparateLines = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set2")) %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
      dyCrosshair(direction = "vertical") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  mh2_g

```
   
*** 
<font size="5">**Lonely**</font>    

In the past 7 days, how often have you felt lonely?  

``` {r mh3}
mh3_g <- dygraph(mh3, main = "", group = "Siaya County Sample") %>%
  dySeries("s6_q3_4", strokeWidth = 4, label = "5-7 days") %>%
  dySeries("s6_q3_3", strokeWidth = 4, label = "3-4 days") %>%
  dySeries("s6_q3_2", strokeWidth = 4, label = "1-2 days") %>%
  dySeries("s6_q3_1", strokeWidth = 4, label = "Not at all or less than one day") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Percentage of sample", drawGrid = FALSE, valueRange = c(0, 110)) %>% 
  dyLegend(width = 450 , labelsSeparateLines = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set2")) %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
      dyCrosshair(direction = "vertical") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  mh3_g

```
   
*** 
<font size="5">**Hopeful about the future**</font>  
    
In the past 7 days, how often have you felt hopeful about the future?  

``` {r mh4}
mh4_g <- dygraph(mh4, main = "", group = "Siaya County Sample") %>%
  dySeries("s6_q4_4", strokeWidth = 4, label = "5-7 days") %>%
  dySeries("s6_q4_3", strokeWidth = 4, label = "3-4 days") %>%
  dySeries("s6_q4_2", strokeWidth = 4, label = "1-2 days") %>%
  dySeries("s6_q4_1", strokeWidth = 4, label = "Not at all or less than one day") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Percentage of sample", drawGrid = FALSE, valueRange = c(0, 110)) %>% 
  dyLegend(width = 450 , labelsSeparateLines = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set2")) %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
      dyCrosshair(direction = "vertical") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  mh4_g

```
   
*** 
<font size="5">**Had physical reactions due to COVID-19**</font>  

  In the past 7 days, how often have you had physical reactions, such as sweating, trouble breathing, nausea, or a pounding heart, when thinking about your experience (e.g., social distancing, loss of income/work, concerns about infection) with the coronavirus/COVID-19 pandemic? 
  
``` {r mh5}
mh5_g <- dygraph(mh5, main = "", group = "Siaya County Sample") %>%
  dySeries("s6_q5_4", strokeWidth = 4, label = "5-7 days") %>%
  dySeries("s6_q5_3", strokeWidth = 4, label = "3-4 days") %>%
  dySeries("s6_q5_2", strokeWidth = 4, label = "1-2 days") %>%
  dySeries("s6_q5_1", strokeWidth = 4, label = "Not at all or less than one day") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Percentage of sample", drawGrid = FALSE, valueRange = c(0, 110)) %>% 
  dyLegend(width = 450 , labelsSeparateLines = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set2")) %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
      dyCrosshair(direction = "vertical") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  mh5_g

```
   
*** 


### Food prices

<font size="5">**Food 1**</font>  
``` {r food1}

pf1_g <- dygraph(pf1, main = "", group = "Siaya County Sample") %>%
  dySeries("mean_price_15", strokeWidth = 4, label = "Beef meat (1kg)") %>%
  dySeries("mean_price_119", strokeWidth = 4, label = "Tilapia fish (whole)") %>%
  dySeries("mean_price_14", strokeWidth = 4, label = "Beans (2kg)") %>%
  dySeries("mean_price_12", strokeWidth = 4, label = "Banana - sweet (bunch)") %>%

  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Price - USD, PPP", drawGrid = FALSE) %>% 
  dyLegend(width = 550 , labelsSeparateLines = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(9, "Set1")) %>%
      dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  pf1_g

```
  
***     

<font size="5">**Food 2**</font>  
``` {r food2}

pf2_g <- dygraph(pf2, main = "", group = "Siaya County Sample") %>%
  dySeries("mean_price_114", strokeWidth = 4, label = "Maize (2kg)") %>%
  dySeries("mean_price_118", strokeWidth = 4, label = "Sugar (1kg)") %>%
  dySeries("mean_price_117", strokeWidth = 4, label = "Rice (1kg)") %>%
  dySeries("mean_price_19", strokeWidth = 4, label = "Cooking fat (500g)") %>%

  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Price - USD, PPP", drawGrid = FALSE) %>% 
  dyLegend(width = 500 , labelsSeparateLines = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set2")) %>%
      dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  pf2_g

```
  
***       

<font size="5">**Food 3**</font>  
``` {r food3}

pf3_g <- dygraph(pf3, main = "", group = "Siaya County Sample") %>%
  dySeries("mean_price_120", strokeWidth = 4, label = "Tomatoes (4)") %>%
  dySeries("mean_price_115", strokeWidth = 4, label = "Onions (4)") %>%
  dySeries("mean_price_110", strokeWidth = 4, label = "Egg (1)") %>%

  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Price - USD, PPP", drawGrid = FALSE) %>% 
  dyLegend(width = 300 , labelsSeparateLines = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(9, "Set1")) %>%
      dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  pf3_g

```
  
***    

### Other prices

<font size="5">**Services**</font>  
``` {r services}

ps_g <- dygraph(ps, main = "", group = "Siaya County Sample") %>%
  dySeries("mean_price_11", strokeWidth = 4, label = "Adult head shaving (1)") %>%
  dySeries("mean_price_111", strokeWidth = 4, label = "Fixing a small hole at a tailor (1)") %>%
  dySeries("mean_price_113", strokeWidth = 4, label = "Grinding 1kg of maize") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Price - USD, PPP", drawGrid = FALSE) %>% 
  dyLegend(width = 250 , labelsSeparateLines = TRUE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set2")) %>%
      dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  ps_g

```
  
***  

<font size="5">**Livestock**</font>  
``` {r livestock}

pl_g <- dygraph(pl, main = "", group = "Siaya County Sample") %>%
  dySeries("mean_price_16", strokeWidth = 4, label = "Calf - local (1)") %>%
  dySeries("mean_price_112", strokeWidth = 4, label = "Goat (1)") %>%
  dySeries("mean_price_18", strokeWidth = 4, label = "Chicken hen (1)") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Price - USD, PPP", drawGrid = FALSE) %>% 
  dyLegend(width = 400 , labelsSeparateLines = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set2")) %>%
      dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  pl_g

```
  
  ***   
    

<font size="5">**Non-food**</font>  
``` {r nonfood}

pnf_g <- dygraph(pnf, main = "", group = "Siaya County Sample") %>%
  dySeries("mean_price_13", strokeWidth = 4, label = "Bar soap (1)") %>%
  dySeries("mean_price_17", strokeWidth = 4, label = "Charcoal (2kg)") %>%
  dySeries("mean_price_116", strokeWidth = 4, label = "Panadol (pair)") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Price - USD, PPP", drawGrid = FALSE) %>% 
  dyLegend(width = 400 , labelsSeparateLines = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set2")) %>%
      dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("8", text = "May 30") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  pnf_g

```
  
***     

### Heat Maps

<font size="5">**Price Index**</font>
```{r price_index_heatmap}
g <- list(
  fitbounds = "locations",
  visible = FALSE,
  showcountries = TRUE,
  showsubunits = TRUE,
  subunitcolor = "gray85",
  bgcolor = "cornsilk"
)
fig <- covid_price_index %>% plot_ly() 
fig <- fig %>% add_trace(
    type="choropleth",
    geojson=json_file,
    locations= ~subloc_name,
    z= ~`Price Index`,
    colorscale="Viridis",
    featureidkey="properties.sublocat_1",
    frame = ~week,
    zmin=88,
    zmax=140
  )
fig <- fig %>% layout(
    geo = g
  )
fig <- fig %>% colorbar(title = "Price Index")
fig <- fig %>% layout(
    title = "Price Index"
) %>% animation_opts(frame = 2000, transition = 500)
fig
```

 ***   
    

<font size="5">**Total Consumption**</font>  
```{r total_consumption_heatmap}
g <- list(
  fitbounds = "locations",
  visible = FALSE,
  showcountries = TRUE,
  showsubunits = TRUE,
  subunitcolor = "gray85",
  bgcolor = "cornsilk"
)
fig <- covid_subloc %>% plot_ly() 
fig <- fig %>% add_trace(
    type="choropleth",
    geojson=json_file,
    locations= ~subloc_name,
    z= ~`Total Consumption`,
    colorscale="Viridis",
    featureidkey="properties.sublocat_1",
    frame = ~week,
    zmin=0,
    zmax=25
  )
fig <- fig %>% layout(
    geo = g
  )
fig <- fig %>% colorbar(title = "Total Consumption")
fig <- fig %>% layout(
    title = "Total Consumption"
) %>% animation_opts(frame = 2000, transition = 500)
fig
```


 ***   
    

<font size="5">**Face Mask Usage**</font>  
```{r face_mask}
g <- list(
  fitbounds = "locations",
  visible = FALSE,
  showcountries = TRUE,
  showsubunits = TRUE,
  subunitcolor = "gray85",
  bgcolor = "cornsilk"
)
fig <- covid_subloc %>% plot_ly() 
fig <- fig %>% add_trace(
    type="choropleth",
    geojson=json_file,
    locations= ~subloc_name,
    z= ~`Face mask usage`,
    colorscale="Viridis",
    featureidkey="properties.sublocat_1",
    frame = ~week,
    zmin=0,
    zmax=100
  )
fig <- fig %>% layout(
    geo = g
  )
fig <- fig %>% colorbar(title = "Face mask usage")
fig <- fig %>% layout(
    title = "Face mask usage"
) %>% animation_opts(frame = 2000, transition = 500)
fig
```

## {}
      
These data comes from phone survey interviews conducted by [REMIT Kenya](http://remitkenya.co.ke/) in Siaya County, Kenya. We are collecting data for a sample of ~12,000 households in the county, which is representative of the whole population. At the same time, our weekly sampling method assures weekly representativeness of the overall sample.

So far we have interviewed 8,293 households, with the following distribution per week:

| Week	| Dates	| Number of surveys |
|------|:-----:|:---------:|
| Week 1 |	05 April 2020 - 11 April 2020	| 745 |
| Week 2 |	12 April 2020 - 18 April 2020	| 744 |
| Week 3 |	19 April 2020 - 25 April 2020	| 1,478 |
| Week 4 |	26 April 2020 - 02 May 2020	| 1,146 |
| Week 5 |	03 May 2020 - 09 May 2020	| 1,499 |
| Week 6 |	10 May 2020 - 16 May 2020	| 986 |
| Week 7 |	17 May 2020 - 23 May 2020	| 1,217 |  
| Week 8 |	24 May 2020 - 30 May 2020	| 478 |



