---
title: "Weekly Statistics"
author: 'Siaya County - Enterprise Sample'
date: ''
output:
  html_document:
    theme: paper
    toc: FALSE
    includes: 
      before_body: header.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(haven)
library(tidyverse)
library(dygraphs)
library(xts)


ent_weekly <- read_dta("../../GE_Endline2/covid19/data/COVID_AllENTs_outcomes_weekly.dta")
ent_outcomes <- read_dta("../../GE_Endline2/covid19/data/COVID_AllENTs_outcomes.dta") #to get retrospective vars
ent_weekly_sector <- read_dta("../../GE_Endline2/covid19/data/COVID_AllENTs_outcomes_weekly_sector.dta")
ent_weekly_sector_n <- read_dta("../../GE_Endline2/covid19/data/COVID_AllENTs_outcomes_weekly_sector_normalized.dta")
ent_weekly_subsector <- read_dta("../../GE_Endline2/covid19/data/COVID_AllENTs_outcomes_weekly_subsector.dta")
covid_weekly <- read_dta("../../GE_Endline2/covid19/data/COVID_AllHHs_outcomes_weekly_c.dta")


#Grouping vars for graphs
rev <- c("week", "rev_wins")
rev <- ent_weekly[rev]

profits <- c("week", "profits_wins")
profits <- ent_weekly[profits]

op <- c("week", "op", "temp_closed", "perm_closed")
op <- ent_weekly[op]

op_hrs <- c("week", "s3_q5_emphrs_p7_wins")
op_hrs <- ent_weekly[op_hrs]

inv <- c("week", "investment_wins")
inv <- ent_weekly[inv]

wages <- c("week", "wages_wins")
wages <- ent_weekly[wages]

cov <- c("week", "ecov_1", "ecov_2", "ecov_3")
cov <- ent_weekly[cov]

bm <- c("week", "bm_emp", "bm_cust")
bm <- ent_weekly[bm]

loan <- c("week", "s_loan", "s_gov", "s_ngo")
loan <- ent_weekly[loan]

cust <- c("week", "s3_q10_customers_p7")
cust <- ent_weekly[cust]

cust_d <- c("week", "for_customers", "loc_customers")
cust_d <- ent_weekly[cust_d]

wfh <- c("week", "wfh_1", "wfh_2")
wfh <- ent_weekly[wfh]

mob <- c("week", "s3_q16a_mobilesales", "mob_money")
mob <- ent_weekly[mob]

presAnnotation <- function(dygraph, x, text) {
  dygraph %>%
    dyAnnotation(x, text, attachAtBottom = TRUE, width = 60, height = 25)
}

##### Create dataframe with retrospective data on profits and revenues
rev_prof <- ent_weekly[c("week", "rev_wins", "profits_wins")]
r_feb <- weighted.mean(ent_outcomes$rev_feb_wins,ent_outcomes$ent_weight,na.rm = TRUE) # Weighted average of feb vars
r_mar <- weighted.mean(ent_outcomes$rev_mar_wins,ent_outcomes$ent_weight,na.rm = TRUE)
r_apr <- weighted.mean(ent_outcomes$rev_apr_wins,ent_outcomes$ent_weight,na.rm = TRUE)
p_feb <- weighted.mean(ent_outcomes$profits_feb_wins,ent_outcomes$ent_weight,na.rm = TRUE)
p_mar <- weighted.mean(ent_outcomes$profits_mar_wins,ent_outcomes$ent_weight,na.rm = TRUE)
p_apr <- weighted.mean(ent_outcomes$profits_apr_wins,ent_outcomes$ent_weight,na.rm = TRUE)
tmp <- data.frame("week" = c(-11,-10,-9,-7,-6,-3),
                  "rev_wins" = c(NA,r_feb,NA, r_mar,NA, r_apr),
                  "profits_wins" = c(NA,p_feb,NA, p_mar,NA, p_apr))
rev_prof <- rbind(tmp, rev_prof)
#rev_prof[13,] <- c(6, NA, NA)

############ Create dataframe of revenues by sector ###############
## Re-shape data for graphs
ag <- covid_weekly[c("week", "i1_wins")]
ag$week <- ag$week -5
ag <- ag[ag$week < 5,]
rt <- ent_weekly_sector[ent_weekly_sector$sector == 1,][c("week", "rev_wins_wins_wins")]
mf <- ent_weekly_sector[ent_weekly_sector$sector == 2,][c("week", "rev_wins_wins_wins")]
sr <- ent_weekly_sector[ent_weekly_sector$sector == 3,][c("week", "rev_wins_wins_wins")]
tmp <- merge(rt,mf, by = "week", all = TRUE, suffixes = c("_rt","_mf"))
tmp <- merge(tmp, sr, by = "week", all = TRUE)
tmp <- merge(tmp, ag, by = "week", all = TRUE)

r_rt_feb <- weighted.mean(ent_outcomes[ent_outcomes$sector == 1,]$rev_feb_wins,ent_outcomes[ent_outcomes$sector == 1,]$ent_weight,na.rm = TRUE)
r_rt_mar <- weighted.mean(ent_outcomes[ent_outcomes$sector == 1,]$rev_mar_wins,ent_outcomes[ent_outcomes$sector == 1,]$ent_weight,na.rm = TRUE)
r_rt_apr <- weighted.mean(ent_outcomes[ent_outcomes$sector == 1,]$rev_apr_wins,ent_outcomes[ent_outcomes$sector == 1,]$ent_weight,na.rm = TRUE)

r_mf_feb <- weighted.mean(ent_outcomes[ent_outcomes$sector == 2,]$rev_feb_wins,ent_outcomes[ent_outcomes$sector == 2,]$ent_weight,na.rm = TRUE)
r_mf_mar <- weighted.mean(ent_outcomes[ent_outcomes$sector == 2,]$rev_mar_wins,ent_outcomes[ent_outcomes$sector == 2,]$ent_weight,na.rm = TRUE)
r_mf_apr <- weighted.mean(ent_outcomes[ent_outcomes$sector == 2,]$rev_apr_wins,ent_outcomes[ent_outcomes$sector == 2,]$ent_weight,na.rm = TRUE)

r_sr_feb <- weighted.mean(ent_outcomes[ent_outcomes$sector == 3,]$rev_feb_wins,ent_outcomes[ent_outcomes$sector == 3,]$ent_weight,na.rm = TRUE)
r_sr_mar <- weighted.mean(ent_outcomes[ent_outcomes$sector == 3,]$rev_mar_wins,ent_outcomes[ent_outcomes$sector == 3,]$ent_weight,na.rm = TRUE)
r_sr_apr <- weighted.mean(ent_outcomes[ent_outcomes$sector == 3,]$rev_apr_wins,ent_outcomes[ent_outcomes$sector == 3,]$ent_weight,na.rm = TRUE)

rev_prof_s <- data.frame("week" = c(-11,-10,-9,-7,-6,-3),
                  "rev_wins_wins_wins_rt" = c(NA,r_rt_feb,NA,r_rt_mar,NA,r_rt_apr), # Programatically updates
                  "rev_wins_wins_wins_mf" = c(NA,r_mf_feb,NA,r_mf_mar,NA,r_mf_apr),
                  "rev_wins_wins_wins" = c(NA,r_sr_feb,NA, r_sr_mar,NA,r_sr_apr),
                  "i1_wins" = c(NA, NA, NA,NA,NA,NA))
#rev_prof_s <- data.frame("week" = c(-11,-10,-9,-7,-6,-3),
#                  "rev_wins_wins_wins_rt" = c(NA,223.6966,NA,162.1954,NA,138.2139), #Using dta from first 4 weeks
#                  "rev_wins_wins_wins_mf" = c(NA,208.973,NA,128.6016,NA,109.5862),
#                  "rev_wins_wins_wins" = c(NA,137.3485,NA, 89.91359,NA,79.15799),
#                  "i1_wins" = c(NA, NA, NA,NA,NA,NA))
rev_prof_s <- rbind(rev_prof_s, tmp)
rev_prof_s$rev_wins_wins_wins_rt <- rev_prof_s$rev_wins_wins_wins_rt*100/r_rt_feb
rev_prof_s$rev_wins_wins_wins_mf <- rev_prof_s$rev_wins_wins_wins_mf*100/r_mf_feb
rev_prof_s$rev_wins_wins_wins <- rev_prof_s$rev_wins_wins_wins*100/r_sr_feb
rev_prof_s$i1_wins <- rev_prof_s$i1_wins*100/.8220776
#rev_prof_s <- rbind(rev_prof_s, c(6, NA, NA, NA,NA,NA))
# Take two week averages (reduce noise)
tmp <- rev_prof_s[1:8,]
tmp <- rbind(tmp,(rev_prof_s[9,]+rev_prof_s[10,])/2)
tmp <- rbind(tmp,(rev_prof_s[11,]+rev_prof_s[12,])/2)
tmp <- rbind(tmp,(rev_prof_s[13,]+rev_prof_s[14,])/2)
tmp <- rbind(tmp,(rev_prof_s[15,]+rev_prof_s[16,])/2)
tmp <- rbind(tmp,(rev_prof_s[17,]+rev_prof_s[18,])/2)
#tmp <- rbind(tmp, rev_prof_s[19,]) # Data from week 7 is very volatile... (fewer obs...) Update once data comes in
tmp <- rbind(tmp, c(7, NA,NA,NA,NA))
rev_prof_s <- tmp


############## Create DF for Investment / Wages ################
i_feb <- weighted.mean(ent_outcomes[ent_outcomes$week != 5,][,"investment_feb_wins"],ent_outcomes[ent_outcomes$week != 5,][,"ent_weight"],na.rm = TRUE)
w_feb <- weighted.mean(ent_outcomes[ent_outcomes$week != 5,][,"wages_feb_wins"],ent_outcomes[ent_outcomes$week != 5,][,"ent_weight"],na.rm = TRUE)
tmp <- data.frame("week" = c(-1),
                  "investment_wins" = c(i_feb)) #alternatively, 2.291782 if we restrict for first weeks only.
inv <- rbind(inv[inv$week < 7,], c(7, NA)) ## Exclude week 7 since very few data points
inv_r <- rbind(tmp,inv)
inv_r <- rbind(c(-2,NA), inv_r)
tmp <- data.frame("week" = c(-1),
                  "wages_wins" = c(w_feb)) #alternatively, 28.96816 if we restrict for first weeks only.
wages_r <- rbind(tmp,wages)
wages_r <- rbind(c(-2,NA), wages_r)

#### Create operating enterprise table with retro. data
op_feb <- weighted.mean(ent_outcomes$op_feb,ent_outcomes$ent_weight,na.rm = TRUE)*100
op_mar <- weighted.mean(ent_outcomes$op_mar,ent_outcomes$ent_weight,na.rm = TRUE)*100
op_apr <- weighted.mean(ent_outcomes$op_apr,ent_outcomes$ent_weight,na.rm = TRUE)*100
op_may <- weighted.mean(ent_outcomes$op_may,ent_outcomes$ent_weight,na.rm = TRUE)*100
op <- op[c("week", "op")]
tmp <- data.frame("week" = c(-14,-13.1,-11,-8.8,-6,-4.5),
                  "op" = c(NA, op_feb, NA, op_mar, NA, op_apr))
op <- rbind(tmp,op)
```
  
##  {.tabset}

### Operations

<font size="5">**Enterprises operating each week**</font> 

``` {r op}
  op_g <- dygraph(op, main = "") %>%
#  dySeries("perm_closed", strokeWidth = 4, label = "Permanently closed") %>%
#  dySeries("temp_closed", strokeWidth = 4, label = "Temporarily closed") %>%
  dySeries("op", strokeWidth = 4, label = "Operational", color = "rgb(78,125,219)") %>%
  dyAxis("x", pixelsPerLabel = 90 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "% Operating enterprises", drawGrid = FALSE, valueRange = c(60, 100)) %>% 
  dyLegend(width = 500, labelsSeparateLines = FALSE) %>%
  dyOptions(stackedGraph = FALSE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4,
            connectSeparatedPoints = TRUE) %>%
    dyCrosshair(direction = "vertical") %>%
    dyEvent(4.1 , "June", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
  dyEvent(-0.2 , "May", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
    dyEvent(-4.5 , "April", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
    dyEvent(-8.8 , "March", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
   dyEvent(-13.1 , "February", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
   dyEvent(-7 , "Lockdown begins", labelLoc = "top") %>%
  presAnnotation("1", text = "May 10") %>%
  presAnnotation("7", text = "June 27") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
op_g
```

February, March and April data points assume that no business that closed down up until that point reopened, and they correspond to the first day of each month. 

*** 

<font size="5">**Total hours worked by all employees - past 7 days**</font> 

``` {r op_hrs}
  op_hrs_g <- dygraph(op_hrs, main = "") %>%
#  dySeries("perm_closed", strokeWidth = 4, label = "Permanently closed") %>%
  dySeries("s3_q5_emphrs_p7_wins", strokeWidth = 4, label = "Hours worked, all employees", color = "rgb(204,0,0)") %>%
  dyAxis("x", pixelsPerLabel = 90 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Hours", drawGrid = FALSE, valueRange = c(52, 68)) %>% 
  dyLegend(width = 500, labelsSeparateLines = FALSE) %>%
  dyOptions(stackedGraph = FALSE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4,
            connectSeparatedPoints = TRUE) %>%
    dyCrosshair(direction = "vertical") %>%
    dyEvent(4.1 , "June", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
  dyEvent(-0.2 , "May", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
    dyEvent(-4.5 , "April", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
    dyEvent(-8.8 , "March", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
   dyEvent(-13.1 , "February", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
   dyEvent(-7 , "Lockdown begins", labelLoc = "top") %>%
  presAnnotation("1", text = "May 10") %>%
  presAnnotation("7", text = "June 27") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
op_hrs_g
```

*** 

<font size="5">**Closures by month relative to February's operation levels**</font> 

```{r}
closed <- data.frame("Month" = c("January", "February", "March", "April", "May",
                                 "January", "February", "March", "April", "May"),
                  "Proportion" = c((47/2797)*100, (43/2797)*100, (230/2797)*100, (168/2797)*100, ((45+39)/2797)*100,
                                   (15/2797)*100, (3/2797)*100, (6/2797)*100, (1/2797)*100, ((0)/2797)*100),
                  "Closed" = c("Temporarily", "Temporarily", "Temporarily","Temporarily","Temporarily",
                                "Permanently", "Permanently","Permanently", "Permanently", "Permanently"))
closed$Month <- factor(closed$Month, levels = c("January", "February", "March", "April", "May"))

ggplot(closed, aes(Month, Proportion)) + geom_col(aes(fill = Closed)) + ylab("% Business closures")+ theme_classic()
```


*** 
### Revenue and profit  
<font size="5">**Enterprises revenue and profits - past 14 days**</font>
```{r enter}
e_g  <- dygraph(rev_prof, main = "") %>%
  dySeries("rev_wins", strokeWidth = 4, label = "Total enterprise revenue" , color = "rgb(78,125,219)") %>%
  dySeries("profits_wins", strokeWidth = 4, label = "Total enterprise profits" , color = "rgb(204,0,0)") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Survey Week") %>% #grid
  dyAxis("y", drawGrid = FALSE , label = "USD, PPP") %>% 
  dyOptions(axisLineWidth = 4, includeZero = TRUE,drawPoints = TRUE, pointSize = 4, connectSeparatedPoints = TRUE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyEvent(-0.2 , "May", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
    dyEvent(-4.5 , "April", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
    dyEvent(-8.8 , "March", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
      dyEvent(4.1 , "June", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
    dyEvent(-7 , "Lockdown begins", labelLoc = "top") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyLegend(width = 200, labelsSeparateLines = TRUE) 
e_g
```

*** 
<font size="5">**Revenue by sector - past 14 days (2 week average)**</font>
```{r}
e_g  <- dygraph(rev_prof_s, main = "") %>%
  dySeries("rev_wins_wins_wins", strokeWidth = 4, label = "Services", color = "rgb(78,125,219)") %>%
  dySeries("rev_wins_wins_wins_rt", strokeWidth = 4, label = "Retail", color = "darkgreen") %>%
  dySeries("rev_wins_wins_wins_mf", strokeWidth = 4, label = "Manufacturing", color = "rgb(204,0,0)") %>%
  dySeries("i1_wins", strokeWidth = 4, label = "Agriculture*", color = "rgb(102,0,204)") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Survey Week") %>% #grid
  dyAxis("y", drawGrid = FALSE , label = "Normalized revenue") %>% 
  dyOptions(axisLineWidth = 4, includeZero = TRUE,drawPoints = TRUE, pointSize = 4, connectSeparatedPoints = TRUE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyEvent(-0.2 , "May", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
    dyEvent(-4.5 , "April", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
    dyEvent(-8.8 , "March", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
      dyEvent(4.1 , "June", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
    dyEvent(-7 , "Lockdown begins", labelLoc = "top") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyLegend(width = 200, labelsSeparateLines = TRUE) 
e_g
``` 

\*Agriculture is normalized by last year's 2-week typical revenue, while all other variables are normalized by the average reported revenue for February. Reported amounts were averaged every two weeks. 

*** 

### External funding

<font size="5">**Enterprises reporting external funding since February 2020**</font>
``` {r loan}
  loan_g <- dygraph(loan, main = "") %>%
  dySeries("s_loan", strokeWidth = 4, label = "Loan", color = "rgb(78,125,219)") %>%
  dySeries("s_gov", strokeWidth = 4, label = "Government assistance", color = "rgb(204,0,0)") %>%
  dySeries("s_ngo", strokeWidth = 4, label = "NGO assistance", color = "darkgreen") %>%
  dyAxis("x", pixelsPerLabel = 90 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "% that received external funding", drawGrid = FALSE, valueRange = c(0, 22)) %>% 
  dyLegend(width = 500, labelsSeparateLines = FALSE) %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4,
            connectSeparatedPoints = TRUE) %>%
    dyCrosshair(direction = "vertical") %>%
    dyEvent(4.1 , "June", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
  dyEvent(-0.2 , "May", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
    dyEvent(-4.5 , "April", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
    dyEvent(-8.8 , "March", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
   dyEvent(-13.1 , "February", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
   dyEvent(-7 , "Lockdown begins", labelLoc = "top") %>%
  presAnnotation("1", text = "May 10") %>%
  presAnnotation("7", text = "June 27") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
loan_g
```

*** 

### Investment and wages

<font size="5">**Investment (USD, PPP) - past 14 days**</font>
``` {r invest}
  inv_g <- dygraph(inv_r, main = "") %>%
  dySeries("investment_wins", strokeWidth = 4, label = "Investment") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Survey Week") %>% #grid
  dyAxis("y", label = "USD, PPP", drawGrid = FALSE) %>% 
  dyLegend(width = 250, labelsSeparateLines = FALSE) %>%
  dyOptions(stackedGraph = FALSE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set1"), connectSeparatedPoints = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "May 10") %>%
  presAnnotation("6", text = "June 20") %>%
#  presAnnotation("-10", text = "February") %>%
  dyEvent(-1 , "February", labelLoc = "bottom", color = "gray", strokePattern = "solid") %>%
    dyEvent(-0.5 , "Lockdown begins March 15", labelLoc = "bottom") %>%
#    dyEvent(-5 , "Dusk-to-dawn curfew imposed", labelLoc = "top") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
inv_g
```
  
  ***  
  
  
<font size="5">**Wages (USD, PPP) - past 14 days**</font>
``` {r wages}
  wages_g <- dygraph(wages_r, main = "") %>%
  dySeries("wages_wins", strokeWidth = 4, label = "Wages") %>%
  dyAxis("x", pixelsPerLabel = 50 , drawGrid = FALSE, label = "Survey Week") %>% #grid
  dyAxis("y", label = "USD, PPP", drawGrid = FALSE) %>% 
  dyLegend(width = 250, labelsSeparateLines = FALSE) %>%
  dyOptions(stackedGraph = FALSE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set2"), connectSeparatedPoints = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "May 10") %>%
  presAnnotation("7", text = "June 27") %>%
  presAnnotation("-10", text = "February") %>%
    dyEvent(-1 , "February", labelLoc = "bottom", color = "gray", strokePattern = "solid") %>%
    dyEvent(-0.5 , "Lockdown begins March 15", labelLoc = "bottom") %>%
    dyEvent(-7 , "Lockdown begins", labelLoc = "top") %>%
    dyEvent(-5 , "Dusk-to-dawn curfew imposed", labelLoc = "top") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
wages_g
```

  
***     


### COVID-19 Impact
<font size="5">**COVID-19 Impact**</font>

How has COVID-19 affected this business?*  

``` {r ecov}
  ecov_g <- dygraph(cov, main = "") %>%
  dySeries("ecov_1", strokeWidth = 4, label = "Reduction in demand/customers") %>%
  dySeries("ecov_2", strokeWidth = 4, label = "Has not affected") %>%
  dySeries("ecov_3", strokeWidth = 4, label = "Other") %>%
  dyAxis("x", pixelsPerLabel = 90 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Percentage of sample", drawGrid = FALSE) %>% 
  dyLegend(width = 500, labelsSeparateLines = FALSE) %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set1")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "May 10") %>%
  presAnnotation("7", text = "June 27") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
ecov_g
```
    
*This is for the proportion of enterprises currently operating.  

  *** 

<font size="5">**Number of customers - past 7 days**</font>
``` {r}
  cust_g <- dygraph(cust, main = "") %>%
#  dySeries("perm_closed", strokeWidth = 4, label = "Permanently closed") %>%
#  dySeries("loc_customers", strokeWidth = 4, label = "Local customers", color = "darkgreen") %>%
  dySeries("s3_q10_customers_p7", strokeWidth = 4, label = "Customers", color = "rgb(78,125,219)") %>%
  dyAxis("x", pixelsPerLabel = 90 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Customers, last week", drawGrid = FALSE, valueRange = c(30, 80)) %>% 
  dyLegend(width = 500, labelsSeparateLines = FALSE) %>%
  dyOptions(stackedGraph = FALSE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4) %>%
    dyCrosshair(direction = "vertical") %>%
    dyEvent(4.1 , "June", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
  presAnnotation("1", text = "May 10") %>%
  presAnnotation("7", text = "June 27") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
cust_g
```


  ***  

### COVID-19 Prevention

<font size="5">**Enterprises reporting a preventive change in their business model**</font>

Percentage of enterprises that reported a change in their business model since March 2020 to reduce the risk of employees spreading or contracting the virus as well as changes that reduce customer interactions. 

``` {r}
  bm_g <- dygraph(bm, main = "") %>%
#  dySeries("perm_closed", strokeWidth = 4, label = "Permanently closed") %>%
  dySeries("bm_emp", strokeWidth = 4, label = "Reduce risk to employees", color = "darkgreen") %>%
  dySeries("bm_cust", strokeWidth = 4, label = "Reduce customer interactions", color = "rgb(78,125,219)") %>%
  dyAxis("x", pixelsPerLabel = 90 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Percentage", drawGrid = FALSE, valueRange = c(0, 110)) %>% 
  dyLegend(width = 500, labelsSeparateLines = FALSE) %>%
  dyOptions(stackedGraph = FALSE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4) %>%
    dyCrosshair(direction = "vertical") %>%
    dyEvent(4.1 , "June", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
  presAnnotation("1", text = "May 10") %>%
  presAnnotation("7", text = "June 27") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
bm_g
```

*** 

<font size="5">**Percentage of businesses with employees working from home**</font>
``` {r}
  wfh_g <- dygraph(wfh, main = "") %>%
#  dySeries("perm_closed", strokeWidth = 4, label = "Permanently closed") %>%
  dySeries("wfh_1", strokeWidth = 4, label = "Sometimes or all of the time", color = "darkgreen") %>%
  dySeries("wfh_2", strokeWidth = 4, label = "Never", color = "rgb(78,125,219)") %>%
  dyAxis("x", pixelsPerLabel = 90 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "% Working from home", drawGrid = FALSE, valueRange = c(0, 110)) %>% 
  dyLegend(width = 500, labelsSeparateLines = FALSE) %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4) %>%
    dyCrosshair(direction = "vertical") %>%
    dyEvent(4.1 , "June", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
  presAnnotation("1", text = "May 10") %>%
  presAnnotation("7", text = "June 27") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
wfh_g
```


  *** 

<font size="5">**Mobile Payments**</font>

Percentage of firms accepting mobile payments and their share among firms that accept mobile payments. 

``` {r}
  mob_g <- dygraph(mob, main = "") %>%
#  dySeries("perm_closed", strokeWidth = 4, label = "Permanently closed") %>%
  dySeries("mob_money", strokeWidth = 4, label = "Accepting mobile payments", color = "darkgreen") %>%
  dySeries("s3_q16a_mobilesales", strokeWidth = 4, label = "Share of mobile payments", color = "rgb(78,125,219)") %>%
  dyAxis("x", pixelsPerLabel = 90 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Percentage", drawGrid = FALSE, valueRange = c(0, 70)) %>% 
  dyLegend(width = 500, labelsSeparateLines = FALSE) %>%
  dyOptions(stackedGraph = FALSE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4) %>%
    dyCrosshair(direction = "vertical") %>%
    dyEvent(4.1 , "June", labelLoc = "bottom", strokePattern = "solid", color = "gray") %>%
  presAnnotation("1", text = "May 10") %>%
  presAnnotation("7", text = "June 27") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
mob_g
```

*** 

### Layoffs

<font size="5">**Temporal distribution of layoffs relative to February's employment level**</font>
```{r}
total <- sum(as.numeric(ent_outcomes$s3_q7_num_paid_feb), na.rm = TRUE) + 197 + 107 +8 +107 + 8 + 98
layoffs <- data.frame("Month" = c("January", "February", "March", "April", "May",
                                  "January", "February", "March", "April", "May"),
                  "Frequency" = c((sum(ent_outcomes$s3_q8_laidoff_jan, na.rm = TRUE))*100/total,
                                  (sum(ent_outcomes$s3_q8_laidoff_feb, na.rm = TRUE))*100/total,
                                  (sum(ent_outcomes$s3_q8_laidoff_mar, na.rm = TRUE))*100/total,
                                  (sum(ent_outcomes$s3_q8_laidoff_apr, na.rm = TRUE)+8)*100/total,
                                  (sum(ent_outcomes$s3_q8_laidoff_may, na.rm = TRUE)+8)*100/total,
                                  (sum(ent_outcomes[ent_outcomes$s2_q2_whenclose == 1,][,"s2_q5_num_employees"], 
                                       na.rm = TRUE))*100/total,
                                  (sum(ent_outcomes[ent_outcomes$s2_q2_whenclose == 2,][,"s2_q5_num_employees"], 
                                       na.rm = TRUE))*100/total,
                                  (sum(ent_outcomes[ent_outcomes$s2_q2_whenclose == 3,][,"s2_q5_num_employees"], 
                                      na.rm = TRUE))*100/total,
                                  (sum(ent_outcomes[ent_outcomes$s2_q2_whenclose == 4,][,"s2_q5_num_employees"], 
                                       na.rm = TRUE))*100/total,
                                  (sum(ent_outcomes[(ent_outcomes$s2_q2_whenclose == 8 | ent_outcomes$s2_q2_whenclose == 9),][,"s2_q5_num_employees"], 
                                       na.rm = TRUE))*100/total),
                  "Status" = c("Enterprise operating","Enterprise operating","Enterprise operating","Enterprise operating","Enterprise operating",
                                          "Enterprise closed","Enterprise closed","Enterprise closed","Enterprise closed","Enterprise closed"))
layoffs$Month <- factor(layoffs$Month, levels = c("January", "February", "March", "April", "May"))
ggplot(layoffs, aes(Month, Frequency)) + geom_col(aes(fill = Status)) + ylab("% Layoffs") + theme_classic()
```


*** 


## {}
      
These data comes from phone survey interviews conducted by [REMIT Kenya](http://remitkenya.co.ke/) in Siaya County, Kenya. We are collecting data for a sample of ~5,000 enterprises in the county, which is representative of the whole population of enterprises. At the same time, our weekly sampling method assures weekly representativeness of the overall sample.

So far we have interviewed 3,041 enterprises, with the following distribution per week:

| Week	| Dates	| Number of surveys |
|------|:-----:|:---------:|
| Week 1 |	10 May 2020 - 16 May 2020	| 532 |
| Week 2 |	17 May 2020 - 23 May 2020	| 458 |
| Week 3 |	24 May 2020 - 30 May 2020	| 434 |
| Week 4 |	31 May 2020 - 06 June 2020	| 732 |
| Week 5 |	07 June 2020 - 13 June 2020	| 885 |
| Week 6 | 14 June 2020 - 20 June 2020 | 904 |

