---
title: "Weekly Statistics"
author: 'Siaya County - Household Sample'
date: ''
output:
  html_document:
    theme: paper
    toc: FALSE
    includes: 
      before_body: header.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(haven)
library(tidyverse)
library(dygraphs)
library(xts)
covid_weekly <- read_dta("~/Dropbox (Princeton)/GE_Endline2/covid19/data/COVID_AllHHs_outcomes_weekly.dta")

#Grouping vars for graphs
cov <- c("week", "cov1_wins", "cov3_wins", "cov4_wins")
cov <- covid_weekly[cov]

cov1 <- c("week", "cov1_cough_wins", "cov1_fever_wins", "cov1_tired_wins", "cov1_fever_cough_wins")
cov1 <- covid_weekly[cov1]

ckn <- c("week", "ckn2_wins", "ckn3_wins", "ckn4_wins", "ckn5_wins", "ckn6_wins")
ckn <- covid_weekly[ckn]

ckn2 <- c("week", "ckn2_cough_wins", "ckn2_fever_wins", "ckn2_tired_wins", "ckn2_dbreath_wins")
ckn2 <- covid_weekly[ckn2]

ckn6 <- c("week", "ckn6_washhands_wins", "ckn6_sanitizer_wins", "ckn6_stayhome_wins", "ckn6_mask_wins")
ckn6 <- covid_weekly[ckn6]

c <- c("week", "c1_wins", "c3_wins") #, "c3_wins", "c4_wins"
c <- covid_weekly[c]

i <- c("week", "i1_wins", "i2_wins" , "i3_wins") #, "i4_wins", "i5_wins", "i6_wins"  , "i7_wins"
i <- covid_weekly[i]
d <- c("week", "i7_wins") 
d <- covid_weekly[d]

it <- c("week", "i5a_wins", "i5b_wins" , "i5c_wins")
it <- covid_weekly[it]

f1 <- c("week", "f1_h_shortages_wins", "f1_h_price_wins", "f1_h_income_wins")
f1 <- covid_weekly[f1]


f1a <- c("week", "f1_h_going_wins", "f1_h_reduce_wins", "f1_h_closed_wins")
f1a <- covid_weekly[f1a]

f1_d <- c("week", "f1_d_skippedadult_wins", "f1_d_skippedchild_wins")
f1_d <- covid_weekly[f1_d]

f1_meals <- c("week", "f1_meat_wins", "f1_eggs_wins")
f1_meals <- covid_weekly[f1_meals]

net5 <- c("week", "net5_today_wins", "net5_last7_wins", "net5_last14_wins")
net5 <- covid_weekly[net5]

ch <- c("week", "ch1_wins", "ch2_wins", "ch3_wins")
ch <- covid_weekly[ch]

l <- c("week", "l1_wins", "l2_wins", "l3_wins")
l <- covid_weekly[l]

e <- c("week", "e3_wins", "e4_wins")
e <- covid_weekly[e]

tg <- c("week", "tg1", "tg2", "tg3", "tg4", "tg5")
tg <- covid_weekly[tg]

tp <- c("week", "tp1", "tp2", "tp3")
tp <- covid_weekly[tp]

gv <- c("week", "gv1", "gv2", "gv3")
gv <- covid_weekly[gv]

v <- c("week", "gv4", "gv5")
v <- covid_weekly[v]

presAnnotation <- function(dygraph, x, text) {
  dygraph %>%
    dyAnnotation(x, text, attachAtBottom = TRUE, width = 60, height = 25)
}

```

  
##  {.tabset}

### Income  
<font size="5">**Earnings per capita (USD, PPP) - past 14 days**</font>
``` {r income}
  i_g <- dygraph(i, main = "") %>%
  dySeries("i3_wins", strokeWidth = 4, label = "Wage earnings") %>%
  dySeries("i2_wins", strokeWidth = 4, label = "Self-employment earnings") %>%
  dySeries("i1_wins", strokeWidth = 4, label = "Agricultural earnings") %>%
  #  dySeries("i7_wins", strokeWidth = 4, label = "Dissaving") %>%
  dyAxis("x", pixelsPerLabel = 75 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "USD, PPP", drawGrid = FALSE) %>% 
  dyLegend(width = 250, labelsSeparateLines = TRUE) %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set2")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("7", text = "May 23") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
i_g
```
  

  This plot aggregates income from each of the three earning sources, across all working-age household members, stacking them to add to the average earning per capita, including children, in the past 14 days. If the household does not perceive income from one or more of the sources, those data points are assigned zeros to assure representativeness for the whole population.  
   
***  
  
<font size="5">**Dissaving per capita (USD, PPP) - past 14 days**</font>  

```{r dissaving}
d_g  <- dygraph(d, main = "") %>%
  dySeries("i7_wins", strokeWidth = 4, label = "Dissaving") %>%
  dyAxis("x", pixelsPerLabel = 75 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE , label = "USD, PPP") %>% 
  dyOptions(axisLineWidth = 4, includeZero = TRUE,drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set1")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("7", text = "May 23") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyLegend(width = 210, show="always") 
d_g
```
 The dissaving variable is constructed by adding the value of assets sold and loans taken, and substracting the value of any assets or durables bought.  
   
***  
   
  <font size="5">**Transfers per capita (USD, PPP) - past 14 days**</font>  

```{r transfers}
it_g  <- dygraph(it, main = "") %>%
  dySeries("i5a_wins", strokeWidth = 4, label = "Government") %>%
  dySeries("i5b_wins", strokeWidth = 4, label = "NGO or community group") %>%
  dySeries("i5c_wins", strokeWidth = 4, label = "Politicians") %>%
  dyAxis("x", pixelsPerLabel = 75 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE , label = "USD, PPP") %>% 
  dyOptions(axisLineWidth = 4, includeZero = TRUE,drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set1")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("7", text = "May 23") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyLegend(width = 500, labelsSeparateLines = FALSE) 
it_g
```
  
  We ask whether in the past 14 days anyone in the household received a gift/assistance of money or goods, and its value, from (i) the government, (ii) from a non-governmental organization or community group, or (iii) from an individual politican or government official.  
  
*** 

### Consumption

<font size="5">**Weekly consumption per capita (USD, PPP)**</font>
``` {r consumption}
c_g <- dygraph(c, main = "", group = "Siaya County Sample") %>%
  #dySeries("c4_wins", strokeWidth = 6, label = "Total consumption") %>%
  #dySeries("c2_wins", strokeWidth = 4, label = "Food consumption") %>%
  dySeries("c3_wins", strokeWidth = 4, label = "Non-food expenditure") %>%
  dySeries("c1_wins", strokeWidth = 4, label = "Food expenditure") %>%
  dyAxis("x", pixelsPerLabel = 75 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "USD, PPP", drawGrid = FALSE) %>% 
  dyLegend(width = 200 , labelsSeparateLines = TRUE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set2")) %>%
      dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("7", text = "May 23") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  c_g

```


*** 

### Food Security  
<font size="5">**Number of days skipping meals in the past 7 days**</font>
```{r struggles}
f1_d_g  <- dygraph(f1_d, main = "") %>%
  dySeries("f1_d_skippedadult_wins", strokeWidth = 4, label = "Adults skipped meals") %>%
  dySeries("f1_d_skippedchild_wins", strokeWidth = 4, label = "Children skipped meals") %>%
 # dySeries("f1_d_hungryadult", strokeWidth = 4, label = "Adults gone to bed hungry") %>%
#  dySeries("f1_d_hungrychild", strokeWidth = 4, label = "Children gone to bed hungry") %>%
  dyAxis("x", pixelsPerLabel = 75 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE , label = "Number of days") %>% 
  dyOptions(axisLineWidth = 4, includeZero = TRUE,drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set1")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("7", text = "May 23") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyLegend(width = 210, labelsSeparateLines = TRUE) 
f1_d_g
```
     
***  
  
<font size="5">**Percentage of sample unable to buy usual amount of food due to:**</font>
   
```{r struggles2}
f1_g  <- dygraph(f1, main = "") %>%
  dySeries("f1_h_price_wins", strokeWidth = 4, label = "High food prices") %>%
  dySeries("f1_h_income_wins", strokeWidth = 4, label = "Income drop") %>%
  dySeries("f1_h_shortages_wins", strokeWidth = 4, label = "Shortages in markets") %>%
  dyAxis("x", pixelsPerLabel = 90 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE , label = "Percentage of sample") %>% 
  dyOptions(axisLineWidth = 4, includeZero = TRUE,drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set1")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("3", text = "April 25") %>%
  presAnnotation("7", text = "May 23") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyLegend(width = 450, labelsSeparateLines = FALSE) %>% 
  dyRangeSelector(dateWindow = c("2", "8"))
f1_g
```   
 We ask whether in the past 7 days, any household member was unable to buy the amount of food they usually buy because of: (i) price of food being too high, (ii) household income having dropped, and (iii) shortages in markets.  
  
     
***  
   
   <font size="5">**Other food hardship experiences, percentage of sample**</font>
  
```{r struggles3}
f1a_g  <- dygraph(f1a, main = "") %>%
  dySeries("f1_h_reduce_wins", strokeWidth = 4, label = "Had to reduce meals") %>%
  dySeries("f1_h_going_wins", strokeWidth = 4, label = "Mobility restrictions impede going to market") %>%
  dySeries("f1_h_closed_wins", strokeWidth = 4, label = "Closed food markets") %>%
  dyAxis("x", pixelsPerLabel = 90 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE , label = "Percentage of sample") %>% 
  dyOptions(axisLineWidth = 4, includeZero = TRUE,drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set2")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("3", text = "April 25") %>%
  presAnnotation("7", text = "May 23") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyLegend(width = 475, labelsSeparateLines = FALSE) %>% 
  dyRangeSelector(dateWindow = c("2", "8"))
f1a_g
``` 
 We ask whether in the past 7 days, any household member experienced: (i) having to reduce the number of meals and/or the portion of each meal they would usually eat, (ii) difficulties in going to food markets due to mobility restrictions imposed by government, and (iii) difficulties in buying food due to most food markets being closed.
  
   
***  
### Household enterprises  
<font size="5">**Enterprises revenue and profits in the past 14 days**</font>
```{r enterprises}
e_g  <- dygraph(e, main = "") %>%
  dySeries("e3_wins", strokeWidth = 4, label = "Total enterprise revenue") %>%
  dySeries("e4_wins", strokeWidth = 4, label = "Total enterprise profits") %>%
  dyAxis("x", pixelsPerLabel = 75 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE , label = "USD, PPP") %>% 
  dyOptions(axisLineWidth = 4, includeZero = TRUE,drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set1")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("7", text = "May 23") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyLegend(width = 200, labelsSeparateLines = TRUE) 
e_g
``` 
  
  ***  

### COVID-19  

<font size="5">**Reported COVID-19 Behavior Adoption**</font>
```{r behavior_changes}
  ckn6_g <- dygraph(ckn6, main = "") %>%
    dySeries("ckn6_washhands_wins", strokeWidth = 4, label = "Hand Washing") %>%
    dySeries("ckn6_mask_wins", strokeWidth = 4, label = "Face Mask") %>%    
    dySeries("ckn6_stayhome_wins", strokeWidth = 4, label = "Stay Home") %>%
    dySeries("ckn6_sanitizer_wins", strokeWidth = 4, label = "Hand Sanitizer") %>%
    dyAxis("x", pixelsPerLabel = 75 , drawGrid = FALSE, label = "Weeks") %>% #grid
    dyAxis("y", drawGrid = FALSE, label = "Percentage of sample") %>% #grid
    dyLegend(width = 580) %>%
    dyOptions(axisLineWidth = 4, includeZero = TRUE, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set2")) %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("7", text = "May 23") %>%
    dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
    dyEvent(1.7 , "Face masks mandatory", labelLoc = "bottom") %>%
  dyCrosshair(direction = "vertical")
  ckn6_g
```
   
  We ask respondents whether they have changed their behavior in any way since learning about COVID-19, and if so, how has it changed.
    
***  

<font size="5">**Reported COVID-19 Symptoms, past 14 days**</font>
``` {r symptoms}
  cov1_g <- dygraph(cov1, main = "") %>% 
  dySeries("cov1_fever_wins", strokeWidth = 4, label = "Fever") %>%
  dySeries("cov1_tired_wins", strokeWidth = 4, label = "Tired") %>%
  dySeries("cov1_cough_wins", strokeWidth = 4, label = "Cough") %>%
  dySeries("cov1_fever_cough_wins", strokeWidth = 4, label = "Fever+Cough") %>%
    dyAxis("x", pixelsPerLabel = 75 , drawGrid = FALSE, label = "Weeks") %>% #grid
    dyAxis("y", drawGrid = FALSE, label = "Percentage of sample") %>% #grid
  dyLegend(width = 500) %>%
  dyOptions(axisLineWidth = 4, includeZero = TRUE, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set2")) %>%
    dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("7", text = "May 23") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
  cov1_g
```
  
  
We ask respondents whether they have experienced any illnesses or symptoms of a given list in the past 14 days.  

*** 

<font size="5">**Number of in-person interactions (other than HH members)**</font>
```{r interactions}
net5_g  <- dygraph(net5, main = "") %>%
  dySeries("net5_last14_wins", strokeWidth = 4, label = "In the past 14 days") %>%
  dySeries("net5_last7_wins", strokeWidth = 4, label = "In the past 7 days") %>%
  dySeries("net5_today_wins", strokeWidth = 4, label = "Today") %>%
  dyAxis("x", pixelsPerLabel = 75 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE, label = "Number of people") %>% 
  dyLegend(width = 500) %>%
     dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("7", text = "May 23") %>%
 dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyOptions(axisLineWidth = 4, includeZero = TRUE, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set1"))
net5_g
```
  
  We ask: "Taken together, how many people outside this household have you interacted with in-person?"   

*** 
  
### Labor Supply

<font size="5">**Weekly labor supply (hours per household adult)**</font>
``` {r labor}
l_g <- dygraph(l, main = "", group = "Siaya County Sample") %>%
  dySeries("l1_wins", strokeWidth = 4, label = "Agricultural labor supply") %>%
  dySeries("l2_wins", strokeWidth = 4, label = "Own enterprise labor supply") %>%
  dySeries("l3_wins", strokeWidth = 4, label = "Wage labor supply") %>%
  dyAxis("x", pixelsPerLabel = 75 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Hours per adult household member", drawGrid = FALSE) %>% 
  dyLegend(width = 550 , labelsSeparateLines = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set2")) %>%
      dyCrosshair(direction = "vertical") %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("7", text = "May 23") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  l_g

```
  
  This plot aggregates hours worked on each of the three sources, across all working-age household members, stacking them to add to the average weekly labor supply per household adult. If the household does not work any hours on one or more of the labor categories, those data points are assigned zeros to assure representativeness of the whole population. 

***  
### Children Education  

<font size="5">**Children educational activities**</font>  
  
```{r children}
ch_g  <- dygraph(ch, main = "", group = "Siaya County Sample") %>%
  dySeries("ch2_wins", strokeWidth = 4, label = "In the past 24 hours") %>%
  dySeries("ch3_wins", strokeWidth = 4, label = "Attended school") %>%
  dySeries("ch1_wins", strokeWidth = 4, label = "In the past 15 minutes") %>%
  dyAxis("x", pixelsPerLabel = 75 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE, label = "Percentage of sample") %>% 
     dyCrosshair(direction = "vertical") %>%
 dyLegend(width = 550) %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("7", text = "May 23") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyOptions(axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set1"))
ch_g
```
   
   We ask what has each child been doing over the last 15 minutes, whether the child has done any learning-related activities in the past 24 hours, and if so, what kind of activity.  
   
   
***  
  
### Household Violence


<font size="5">**Gender violence**</font>

We ask married/cohabitant female respondents whether their husband/partners have (i) threaten to harm them or someone close to them, (ii) hit, slapped, kicked, or physically hurt them, and (iii) forced them to perform sexual acts.*  
```{r gender}
gv_g  <- dygraph(gv, main = "", group = "Siaya County Sample") %>%
  dySeries("gv1", strokeWidth = 4, label = "Threaten to harm them") %>%
  dySeries("gv2", strokeWidth = 4, label = "Physically hurt them") %>%
  dySeries("gv3", strokeWidth = 4, label = "Forced them to perform sexual acts") %>%
  dyAxis("x", pixelsPerLabel = 75 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE, label = "Percentage of married/cohabitant females") %>% 
     dyCrosshair(direction = "vertical") %>%
 dyLegend(width = 580) %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("7", text = "May 23") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyOptions(axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set1"))
gv_g
```
  *This plot shows data only for the share of female respondents that were surveyed by a female field officer, and are currently married or living with a partner. This sub-sample accounts for ~55% of all married/cohabitant females in the study sample, and ~36% of all females.  
     
***  
  
<font size="5">**Violence in the household**</font>  
We ask: (i) Over the past 14 days, has there been a higher than usual amount of fights with members of your household?, and (ii) In the past 14 days, did you or your partner ever beat any of the children living in this household?  
```{r violence}
v_g  <- dygraph(v, main = "", group = "Siaya County Sample") %>%
  dySeries("gv4", strokeWidth = 4, label = "Children were beaten") %>%
  dySeries("gv5", strokeWidth = 4, label = "More fights than usual") %>%
  dyAxis("x", pixelsPerLabel = 75 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", drawGrid = FALSE, label = "Percentage of sample") %>% 
     dyCrosshair(direction = "vertical") %>%
 dyLegend(width = 350) %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("7", text = "May 23") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>%
  dyOptions(axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(4, "Set1"))
v_g
```


***  

### Trust

<font size="5">**Trust in government**</font>  

How much do you trust your country’s government to take care of its citizens?  
``` {r trustgov}
tg_g <- dygraph(tg, main = "", group = "Siaya County Sample") %>%
  dySeries("tg1", strokeWidth = 4, label = "Strongly distrust") %>%
  dySeries("tg2", strokeWidth = 4, label = "Somewhat distrust") %>%
  dySeries("tg3", strokeWidth = 4, label = "Neither trust nor distrust") %>%
  dySeries("tg4", strokeWidth = 4, label = "Somewhat trust") %>%
  dySeries("tg5", strokeWidth = 4, label = "Strongly trust") %>%
  dyAxis("x", pixelsPerLabel = 75 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Percentage of sample", drawGrid = FALSE, valueRange = c(0, 110)) %>% 
  dyLegend(width = 450 , labelsSeparateLines = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set2")) %>%
  presAnnotation("1", text = "April 11") %>%
  presAnnotation("7", text = "May 23") %>%
      dyCrosshair(direction = "vertical") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  tg_g

```
   
***  
  
  <font size="5">**Trust in other people**</font>  

Generally speaking, would you say that most people can be trusted or that you need to be very careful in dealing with people?  
``` {r trustpeople}

tp_g <- dygraph(tp, main = "", group = "Siaya County Sample") %>%
  dySeries("tp3", strokeWidth = 4, label = "Need to be careful") %>%
  dySeries("tp2", strokeWidth = 4, label = "Most people can be trusted") %>%
  dySeries("tp1", strokeWidth = 4, label = "Don't know") %>%
  dyAxis("x", pixelsPerLabel = 75 , drawGrid = FALSE, label = "Weeks") %>% #grid
  dyAxis("y", label = "Percentage of sample", drawGrid = FALSE, valueRange = c(0, 110)) %>% 
  dyLegend(width = 500 , labelsSeparateLines = FALSE) %>%
    dyCrosshair(direction = "vertical") %>%
  dyOptions(stackedGraph = TRUE, includeZero = TRUE, axisLineWidth = 4, drawPoints = TRUE, pointSize = 4, colors = RColorBrewer::brewer.pal(5, "Set1")) %>%
      dyCrosshair(direction = "vertical") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) 
  tp_g

```

***  

## {}
      
These data comes from phone survey interviews conducted by [REMIT Kenya](http://remitkenya.co.ke/) in Siaya County, Kenya. We are collecting data for a sample of ~12,000 households in the county, which is representative of the whole population. At the same time, our weekly sampling method assures weekly representativeness of the overall sample.

So far we have interviewed 7,812 households, with the following distribution per week:

| Week	| Dates	| Number of surveys |
|------|:-----:|:---------:|
| Week 1 |	05 April 2020 - 11 April 2020	| 745 |
| Week 2 |	12 April 2020 - 18 April 2020	| 744 |
| Week 3 |	19 April 2020 - 25 April 2020	| 1,478 |
| Week 4 |	26 April 2020 - 02 May 2020	| 1,146 |
| Week 5 |	03 May 2020 - 09 May 2020	| 1,499 |
| Week 6 |	10 May 2020 - 16 May 2020	| 986 |
| Week 7 |	17 May 2020 - 23 May 2020	| 1,214 |


